---
title: "Homework 6"
author: "Siyan Wen"
date: "2023-11-30"
output: html_document
---

```{r}
library(tidyverse)
set.seed(1)
```
# Problem 2
#### Download the data.
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
#### Bootstrap and SLR 
```{r}
bootstrap_result_glance=
  weather_df|>
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin +prcp , data = df)),
    results = map(models, broom::glance)) |> 
  select(results) |> 
  unnest(results)
  

bootstrap_result_tidy=
  weather_df|>
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin +prcp , data = df)),
    results = map(models, broom::tidy)) |> 
  select(results) |> 
  unnest(results)|>
  select(term,estimate)|>
  pivot_wider(
    names_from=term,
    values_from=estimate
  )|>
  unnest()

```
#### Show distribution
```{r}
r.squared_distribution=
  bootstrap_result_glance|>
  ggplot(aes(x = r.squared)) + geom_density()
print(r.squared_distribution)

log_distribution=
  bootstrap_result_tidy|>
  mutate(log.value=log10(tmin*prcp))|>
  ggplot(aes(x = log.value)) + geom_density()

print(log_distribution)
```

**Description:**

The distribution of "r.squared" exhibits a notable heavy tail extending to low values. Additionally, there is a slight bump in the distribution, possibly the features mentioned above indicating occasional occurrences of larger outliers within the bootstrap samples. 

The distribution of "log" exhibits a even more notable heavy tail extending to the low values. This is an uni-modal and left/negative skewed distribution. This shows a tendency for the majority of values to cluster on the right side, with a tail extending towards the lower values.

#### Confidence interval
```{r}
bootstrap_result_glance |> 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975))

bootstrap_result_tidy|>
  mutate(log.value=log10(tmin*prcp))|>
  summarize(
    ci_lower_log.value = quantile(log.value, 0.025,na.rm = TRUE), 
    ci_upper_log.value = quantile(log.value, 0.975,na.rm = TRUE)
    )
```
# Problem 3
```{r}
```